Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-30 paper.qmd
still got histograms but a little neater

hex_grid_coloured_scurve1_dens <- ggplot(hex_grid_with_counts_s_curve1) +
  geom_histogram(aes(x=std_counts), binwidth = hb_obj_scurve1$centroids$c_x[2]-hb_obj_scurve1$centroids$c_x[1])
```

@@

hex_grid_coloured_scurve2_dens <- ggplot(hex_grid_with_counts_s_curve2) +
  geom_histogram(aes(x=std_counts), binwidth = hb_obj_scurve2$centroids$c_x[2]-hb_obj_scurve2$centroids$c_x[1])
```

@@

hex_grid_coloured_scurve3_dens <- ggplot(hex_grid_with_counts_s_curve3) +
  geom_histogram(aes(x=std_counts), binwidth = hb_obj_scurve3$centroids$c_x[2]-hb_obj_scurve3$centroids$c_x[1]) 
```

>>>>

hex_grid_coloured_scurve1_dens <- ggplot(hex_grid_with_counts_s_curve1) +
  geom_histogram(aes(x=std_counts), 
                 breaks=seq(0, 1, 0.05),
                 fill="slategray4", colour="white")

#hex_grid_coloured_scurve1_dens <- 
#  hex_grid_with_counts_s_curve1 |>
#  filter(!is.na(std_counts)) |>
#  mutate(ord_std_counts = n() - rank(std_counts)) |>
#  ggplot() +
#  geom_line(aes(x=ord_std_counts, y=std_counts), 
#                 colour="slategray4")
```

@@

hex_grid_coloured_scurve2_dens <- ggplot(hex_grid_with_counts_s_curve2) +
  geom_histogram(aes(x=std_counts), 
                 breaks=seq(0, 1, 0.05),
                 fill="slategray4", colour="white")

#hex_grid_coloured_scurve2_dens <- 
#  hex_grid_with_counts_s_curve2 |>
#  filter(!is.na(std_counts)) |>
#  mutate(ord_std_counts = n() - rank(std_counts)) |>
#  ggplot() +
#  geom_line(aes(x=ord_std_counts, y=std_counts), 
#                 colour="slategray4")

@@

hex_grid_coloured_scurve3_dens <- ggplot(hex_grid_with_counts_s_curve3) +
  geom_histogram(aes(x=std_counts), 
                 breaks=seq(0, 1, 0.05),
                 fill="slategray4", colour="white") 
#hex_grid_coloured_scurve3_dens <- 
#  hex_grid_with_counts_s_curve3 |>
#  filter(!is.na(std_counts)) |>
#  mutate(ord_std_counts = n() - rank(std_counts)) |>
#  ggplot() +
#  geom_line(aes(x=ord_std_counts, y=std_counts), 
#                 colour="slategray4")
```
